### 2017-01-09 paper/evaluation.tex
updated rq3

\Jbc{I'm currently considering only the long group but as soon as I
have the remaining results, I will update the plots} To evaluate the
presence of parallelization settings, we considered the \numMedLong{}
subjects from the \longg{} and \medg{} groups identified in
Section~\ref{sec:rqA}. We focused on these two groups because given
that costly test suites exist, we wanted to investigate if their
maintainers are aware of parallelization settings and how they use
these settings (see Section \ref{sec:modes}).  We computed the
frequency of the parallelism modes using a two-steps approach: the
first step (discovery) automatically finds relevant build files
(\ie, \pomf{} files with parallelization settings); the second step
(inspection) consists in a manual inspection to confirm the presence
of parallelism settings in the build file and classify them according
to the parallelism level (see Section \ref{sec:modes}).
Figure~\ref{fig:discovery-step} describes the discovery step: we list
the paths of all build files and filter only the files that contain
any of the keywords \CodeIn{forkMode}, \CodeIn{forkCount}, or
\CodeIn{parallel}.  Notice that, for Maven projects, any of these
keywords exist in any possible parallel setting \Fix{cite surefire
doc}. Our first step is complete but is not sound since the line that
matches one of keywords may not represent part of a real setting (\eg,
comments).  We eliminate false-positives in the confirmation step.
From the \numMedLong{} subjects, the discovery step found 2853 files
and filtered 109 relevant files. Later, from the 109 relevant files,
we confirmed \Fix{M} valid settings from \Fix{X} subjects.
Table~\ref{tab:inspection-table} summarizes the results from the file
inspection and Figure~\ref{fig:freqmodes} shows the distribution of
parallelism modes from the \Fix{M} settings.

@@

\begin{table}[h!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccccc}
        \toprule%
        Group  & Build Files & Filtered files & Settings & Subjects \\%
        \midrule%
        Long   & 1613 & 79 & \Fix{X} & \Fix{X}\\%
        Medium & 1240 & 30 & \Fix{X} & \Fix{X}\\%
        \midrule%
        Total  & 2853 & 109 & \Fix{X} & \Fix{X}\\%
        \bottomrule%
    \end{tabular*}
    \caption{\Fix{to-be-defined}}
    \label{tab:inspection-table} 
\end{table}

\begin{figure}[h!]
    \centering
    \Fix{to appear}
    \caption{\label{fig:freqmodes}Distribution of parallelism modes
    identified in \Fix{M} }
\end{figure}

>>>>

To evaluate the presence of parallelization settings, we considered
the \numMedLong{} subjects from the \longg{} and \medg{} groups
identified in Section~\ref{sec:rqA}. We focused on these two groups
because given that costly test suites exist, we wanted to investigate
if their maintainers are aware of parallelization settings and how
they use these settings (see Section \ref{sec:modes}).  We computed
the frequency of the parallelism modes using a two-steps approach: the
first step (discovery) automatically finds relevant build files (\ie,
\pomf{} files with parallelization settings); the second step
(inspection) consists in a manual inspection to confirm the presence
of parallelism settings in the build file and classify them according
to the parallelism level (see Section \ref{sec:modes}).
Figure~\ref{fig:discovery-step} describes the discovery step: we list
the paths of all build files and filter only the files that contain
any of the keywords \CodeIn{forkMode}, \CodeIn{forkCount}, or
\CodeIn{parallel}.  Notice that, for Maven projects, any of these
keywords exist in any possible parallel setting \Fix{cite surefire
doc}. Our first step is complete but is not sound since the line that
matches one of keywords may not represent part of a real setting (\eg,
comments).  We eliminate false-positives in the confirmation step.
From the \numMedLong{} subjects, the discovery step found 2853 files
and filtered 109 relevant files. Later, from the 109 relevant files,
we confirmed \Fix{M} valid settings from \Fix{X} subjects.
\Jbc{Elaborate results}
Table~\ref{tab:inspection-table} summarizes the results from the file
inspection and Figure~\ref{fig:freqmodes} shows the distribution of
parallelism modes from the \Fix{M} settings.

@@

\begin{table}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccccc}
        \toprule%
        Group  & Build Files & Filtered files & Settings & Subjects \\%
        \midrule%
        Long   & 1613 & 79 & \Fix{X} & \Fix{X}\\%
        Medium & 1240 & 30 & \Fix{X} & \Fix{X}\\%
        \midrule%
        Total  & 2853 & 109 & \Fix{X} & \Fix{X}\\%
        \bottomrule%
    \end{tabular*}
    \caption{\Fix{to-be-defined}}
    \label{tab:inspection-table} 
\end{table}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallelism modes
    identified in \Fix{M} \Jbc{Currently mocked data}}
\end{figure}

\Jbc{Conclusion and relate the results to the
RQ...........................................}
